MHF SCP Experiment Visualisations

### 2024-09-04 minos/outcomes/MHF_SCP_visualisations.Rmd
Added module for universal_credit

```{r}
scen.colour.list <- c('baseline', '£10', '£20',
               '£25', '£30',
               '£35', '£40', '£45',
               '£50', '£60', '£70',
               '£80', '£90', '£100')

#colours <- display.brewer.all(length(scen.list.full))
#colours <- colorRampPalette( brewer.pal(11,"Spectral") )(14)
colours <- colorRampPalette( brewer.pal(9,"Set1") )(14)
my_palette <- set_names(colours, scen.colour.list)

scen.list.full <- c('baseline', '10UniversalCredit', '20UniversalCredit',
               '25UniversalCredit', '30UniversalCredit',
               '35UniversalCredit', '40UniversalCredit', '45UniversalCredit',
               '50UniversalCredit', '60UniversalCredit', '70UniversalCredit',
               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')

@@

@@

### UC

@@

@@

```{r}

```{r}

```{r}
summary_group <- 'UC_families_men_illness_risk'
scen.list <- scen.list.25_100
palette <- my_palette

mental_illness_risk_plots_interval(summary_group, scen.list, palette)
```

>>>>

```{r}
scen.colour.list <- c('baseline', '£10', '£20',
               '£25', '£30',
               '£35', '£40', '£45',
               '£50', '£60', '£70',
               '£80', '£90', '£100', '£110', '£120', '£130')

#colours <- display.brewer.all(length(scen.list.full))
#colours <- colorRampPalette( brewer.pal(11,"Spectral") )(14)
colours <- colorRampPalette( brewer.pal(9,"Set1") )(17)
my_palette <- set_names(colours, scen.colour.list)

scen.list.full <- c('baseline', '10UniversalCredit', '20UniversalCredit',
               '25UniversalCredit', '30UniversalCredit',
               '35UniversalCredit', '40UniversalCredit', '45UniversalCredit',
               '50UniversalCredit', '60UniversalCredit', '70UniversalCredit',
               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit',
               '110UniversalCredit', '120UniversalCredit', '130UniversalCredit')

@@

scen.list.10_130 <- c('baseline', '10UniversalCredit', '20UniversalCredit',
                      '30UniversalCredit', '40UniversalCredit', '50UniversalCredit', 
                      '60UniversalCredit', '70UniversalCredit', '80UniversalCredit', 
                      '90UniversalCredit', '100UniversalCredit',
                      '110UniversalCredit', '120UniversalCredit', '130UniversalCredit')

@@

@@

## Cost Ratio: £10 - £130

```{r}
SF_12_cost_ratio(summary_type = 'UC', scen_list = scen.list.10_130)
SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.10_130)
```

@@
